Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s07_problempinning.tex
Adjusted a few more figures, glass in particular

\begin{figure}\centering
    \includegraphics[width=0.5\linewidth]{img/Silica}
    \caption{Example of 1 layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins.}
    \label{fig:silica_glass}
\end{figure}

\begin{itemize}
    \item Pin together 2 underconstrained monolayers in such a way that the resulting bilayer becomes isostatic.
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Build the structures by repeated subdivision to ensure they are isostatic at each layer (see Figure \ref{fig:subdivision})
\end{itemize}

@@

\begin{figure}\centering
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[width=\linewidth]{img/pentl3}
    \end{subfigure}
    \caption{An example of self-similarity in the form of repeated subdivisions. Each figure follows fromt he previous due to a set subdivision rule. If each figure was guaranteed to be isostatic, then isostatic systems of arbitrary detail could be made.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}

% \begin{subfigure}

% \end{subfigure}
\caption{(a) is a 1 dof body-pin qusec. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}

>>>>

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica} \hspace{0.5cm}
    \raisebox{0.5\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a signle layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins. Not shown here are other layers stacked on this one. Each Silicon atom has the structure seen to the right, and so binds to another Oxygen atom in another layer.}
    \label{fig:silica_glass}
\end{figure}

\begin{itemize}
    \item Pin together 2 underconstrained monolayers in such a way that the resulting bilayer becomes isostatic (see Figure \ref{fig:silica_glass}).
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Build the structures by repeated subdivision to ensure they are isostatic at each layer (see Figure \ref{fig:subdivision})
\end{itemize}

@@

\begin{figure}\centering
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    % 
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    % 
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[width=\linewidth]{img/pentl3}
    \end{subfigure}
    \caption{An example of self-similarity in the form of repeated subdivisions. Each figure follows fromt he previous due to a set subdivision rule. If each figure was guaranteed to be isostatic, then isostatic systems of arbitrary detail could be made.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1 dof body-pin qusec. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
